Large Linear Multi-output Gaussian Process Learning

### 2017-03-31 paper/paper.tex
spell check

An LMC kernel $K$ is of the form 
\begin{align}
K([i,\Tx_i],[j,\Tx_j])=\sum_{q=1}^Qb_{ij}^{(q)}k_q(\norm{\Tx_i-\Tx_j})+\epsilon_i\delta_{ij},\label{lmcpointwise}
\end{align} 
where $k_q:\R\rightarrow\R$ is a stationary kernel on $\mcX$. Typically, the positive semi-definite (PSD) matrices $B_q\in\R^{D\times D}$ formed by $b_{ij}^{(q)}$ are parameterized as $A_qA_q^\top+\bsk_q I_D$, with $A_q\in\R^{D\times R_q},\bsk_q\in\R_+^D$ and $R_q$ a pre-set rank. Importantly, even though each $k_q$ is stationary, $K$ is only stationary on $\mcX'$ if $B_q$ is Toeplitz. Settings of $B_q$ that arise in practice, where we wish to capture covariance across outputs as an arbitrary $D^2$-dimensional latent process,  prevent stationarity in $K$ and therefore prohibit direct application of SKI.

@@

For a gradient-only stopping heuristic, we maintain the running maximum gradient $\infty$-norm. If gradient norms drop below a pre-set proportion of the running maximum norm more than a pre-set tolerance number of times, we terminate. For example, when applied to the foreign exchange rate prediction (FX2007) dataset in Section~\ref{fx2007-results}, the heuristic eventually notices that we have slowed down increases in $\mcL$ because the gradients occasionally drop below the threshold at that point, while not displacing the solution $\bsth$ significantly since we must be near a local minimum (Fig.~\ref{fx2007-stop}).

@@

>>>>

An LMC kernel $K$ is of the form 
\begin{align}
K([i,\Tx_i],[j,\Tx_j])=\sum_{q=1}^Qb_{ij}^{(q)}k_q(\norm{\Tx_i-\Tx_j})+\epsilon_i\delta_{ij},\label{lmcpointwise}
\end{align} 
where $k_q:\R\rightarrow\R$ is a stationary kernel on $\mcX$. Typically, the positive semi-definite (PSD) matrices $B_q\in\R^{D\times D}$ formed by $b_{ij}^{(q)}$ are parameterized as $A_qA_q^\top+\bsk_q I_D$, with $A_q\in\R^{D\times R_q},\bsk_q\in\R_+^D$ and $R_q$ a preset rank. Importantly, even though each $k_q$ is stationary, $K$ is only stationary on $\mcX'$ if $B_q$ is Toeplitz. Settings of $B_q$ that arise in practice, where we wish to capture covariance across outputs as an arbitrary $D^2$-dimensional latent process,  prevent stationarity in $K$ and therefore prohibit direct application of SKI.

@@

For a gradient-only stopping heuristic, we maintain the running maximum gradient $\infty$-norm. If gradient norms drop below a preset proportion of the running maximum norm more than a pre-set tolerance number of times, we terminate. For example, when applied to the foreign exchange rate prediction (FX2007) dataset in Section~\ref{fx2007-results}, the heuristic eventually notices that we have slowed down increases in $\mcL$ because the gradients occasionally drop below the threshold at that point, while not displacing the solution $\bsth$ significantly since we must be near a local minimum (Fig.~\ref{fx2007-stop}).

@@

%  LocalWords:  Feinberg pu Cheng Engelhardt Kai LLGP Bonilla COGP qA
%  LocalWords:  hyperparameter's nguyen Semiparametric SLFM Scalable
%  LocalWords:  MSGP vectorization matricization parameterization PSD
